Detecci\'on de malas hierbas a trav\'es\\ de t\'ecnicas de redes neuronales convolucionales y visi\'on artificial

### 2017-05-04 PaperBCJ.tex
Without references, Second Part of State of Art

Today the agriculture has many challenges for the Precision Agriculture such as the Weed and Crop segmentation \cite{Brivot:Marchant} ,

>>>>

Today the agriculture has many challenges for the Precision Agriculture such as the Weed and Crop segmentation, according to Suarez, Piñero y Valladores, el yield of the corn is affected by 5000 kg/ha. Actually the growing development of techniques of Artificial Vision and Machine Learning permit to researchers propose solutions for the Segmentation of Weeds in Crops.

One of the first approximations to the algorithms of detection of Crops is the developed in 1996 by Brivot and Mercant, this could be possible by the use of IR Images, the image is processed by a hysteresis umbral and the method of Min Neighbouring to identify the row of crops. In recent years the implementation of Machine Learning has opened new possibilities for differentiate the Weed from the crops, recently Chend and Mason had developed an algorithm by the use of Harris Corner detector, Feature Detector and using the DBSCAN(Density-based spartial clustering of apllications with noise) as Machine Learnin, it demonstrates an effectiveness of  98\% in the identification of Weeds in the Rice.  Hong, Lei and Heping use an optimal method for detection in various types of luminosity, they achived this by the use an ANN for weed and maize classification, with a precision of 92.5\%, Araguez et. al perform their analysis through the analysis of the green hystogram and performing the segmentation of the crop and weed by classifiers not specified in the document. Su Hnin Hlaing1, Aung Soe Khaing used the binarization methods of OTSU and Watershed for the segmentation of the images, while the classification was given through a areas analysis to perform a thresholding, although the method is computationally effective when the Weed distribution does not resemble the size to the crop plant, its error increases when there is more density of crop than of weed. Romeo et. al propose to use a fuzzy clustering approach to correctly segment the crop green and the same algorithm to classify the soil crop. Potena, Nardi and Pretto use a multispectral camera to obtain RGB and NIR images, for the segmentation and classification they use a light CNN for the first process and a Deep CNN for classification, its accuracy is up to 98\%. There is an approximation to Cicco, Potena, Griseeti CNN through the generation of datasets
